---
title: "The DashiellBoard: Tracking Cornell's COVID-19 Data"
date: 'last updated: 02/11/21'
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: embed
---

<style>                     
.navbar {
  background-color:#B31B1B;
  border-color:black;
}
</style>

```{r setup}
library(flexdashboard)    # install.packages('flexdashboard')
library(tidyverse)        # install.packages('tidyverse')
library(zoo)              # install.packages('zoo')
library(lubridate)        # install.packages('lubridate')
library(plotly)           # install.packages('plotly')
```


```{r import}
# Data import
covid <- read_csv('cleaned_covid_data.csv',
                  col_types = 'Ddddd')

### Constants

# Threat levels
green1 <- c(date('2020-08-17'), date('2020-09-03'))
yellow1 <- c(date('2020-09-03'), date('2020-09-15'))
green2 <- c(date('2020-09-15'), date('2020-11-12'))
yellow2 <- c(date('2020-11-12'), date('2020-11-18'))
green3 <- c(date('2020-11-18'), date('2021-02-03'))
yellow3 <- c(date('2021-02-04'), date(max(covid$dates)))

# Colors
color_cumulative <- '#A45C40'
color_14day <- '#C38370'
color_7day <- '#E4B7A0'
threat_color_green <- '#4C7B2B'
threat_color_yellow <- '#F2D21B'

# Icons
icon_positive <- 'ion-ios-plus-outline'
icon_test <- 'ion-search'
```

```{r define-functions}
# Calculate total within a period
calculate_period_total <- function(timescale){
  covid %>%
    filter(dates >= date(now()) - timescale) %>%
             summarize(total_cases = sum(N_cases),
                       total_tests = sum(N_tests))
}

# Calculate rolling summary
calculate_rolling <- function(timescale, func) {
  cases <- rollapply(covid$N_cases, timescale, func)
  tests <- rollapply(covid$N_tests, timescale, func)
  dates <- tail(covid$dates, length(cases))
  tibble(dates, cases, tests)
}

# Calculations for value boxes
total_positives <- sum(covid$N_cases)
total_tests <- sum(covid$N_tests)
total_7day <- calculate_period_total(7)
total_14day <- calculate_period_total(14)
```

```{r plot-elements}
plot_base <- function(x1, x2, y1, y2) {
  ggplot(data = NULL) +
    geom_rect(aes(xmin = x1, xmax = green1[2],
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Green: 8/17-9/2'),
              fill = threat_color_green) +
    geom_rect(aes(xmin = yellow1[1]-0.5, xmax = yellow1[2] + 0.5,
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Yellow: 9/3-9/15'),
              fill = threat_color_yellow) +
    geom_rect(aes(xmin = green2[1]-0.5, xmax = green2[2] + 0.5,
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Green: 9/16-11/12'),
              fill = threat_color_green) +
    geom_rect(aes(xmin = yellow2[1]-0.5, xmax = yellow2[2] + 0.5,
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Yellow: 11/13-11/18'),
              fill = threat_color_yellow) +
    geom_rect(aes(xmin = green3[1]-0.5, xmax = green3[2] + 0.5,
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Green: 11/19-02/04'),
              fill = threat_color_green) +
    geom_rect(aes(xmin = yellow3[1]-0.5, xmax = x2,
                  ymin = y1, ymax = y2,
                  text = 'Threat Level Yellow: 02/04-present'),
              fill = threat_color_yellow) +
    geom_vline(aes(xintercept = as.numeric(as.Date('2020-09-02'))-0.5,
                   text = 'Start of surveillance testing'),
               linetype = 'dotted') + 
    xlab('Date') +
    scale_x_date(date_breaks = '5 days', date_labels = '%b %d',
                 expand = c(0,0), limit = c(x1, x2)) +
    scale_y_continuous(limits = c(y1, y2), expand = c(0,0)) +
    theme(axis.text.x = element_text(angle = 45))
}

convert_to_interactive <- function(plot_name, margin_size) {
  ggplotly(plot_name, tooltip = 'text') %>%
  layout(xaxis = list(fixedrange = TRUE),
         yaxis = list(fixedrange = TRUE),
         margin = list(b = margin_size)) %>%
  config(displayModeBar = F)
}
```

Row
-----------------------------------------------------------------------

### All cases {.value-box}

```{r cumulative-total}
valueBox(value = format(total_positives, big.mark = ','),
         caption = 'Total cases (08/17-present)',
         icon = icon_positive, 
         color = color_cumulative)
```

### 14 day cases {.value-box}

```{r two-week-total}
valueBox(value = format(total_14day$total_cases, big.mark = ','),
         caption = paste0('Cases in the past 2 weeks (',
                          format(date(now())-14, '%m/%d'), '-',
                          format(date(now())-1, '%m/%d'), ')'),
         icon = icon_positive, 
         color = color_14day)
```

### 7 day cases {.value-box}

```{r one-week-total}
valueBox(value = total_7day$total_cases,
         caption = paste0('Cases this week (',
                          format(date(now())-7, '%m/%d'), '-',
                          format(date(now())-1, '%m/%d'), ')'),       
         icon = icon_positive, 
         color = color_7day)
```

### 7 day tests {.value-box}

```{r one-week-tests}
valueBox(value = format(total_7day$total_tests, big.mark = ','),
         caption = paste0('Tests this week (',
                          format(date(now())-7, '%m/%d'), '-',
                          format(date(now())-1, '%m/%d'), ')'),         
         icon = icon_test, 
         color = color_7day)
```

Row {.tabset}
-----------------------------------------------------------------------

### Total cases, cumulative
```{r plot-cumulative}
base_plot <- plot_base(min(covid$dates)-0.5, max(covid$dates)+0.5,
                       -5, total_positives + 15)

plot_cumulative <- base_plot +
        geom_point(data = covid, aes(x = dates, y = cumsum(N_cases),
                       text = paste('Date:', 
                                    format(date(dates),'%m/%d'),
                                    '<br>Cases:', cumsum(N_cases))),
                        color = 'black') +
        ylab('Cumulative Total Positive Tests')
        
    
convert_to_interactive(plot_cumulative, 0)
```

### Positives per day
```{r plot-histogram}

plot_histogram <- ggplot(covid) +
  geom_bar(aes(x = as.Date(dates), y = N_cases,
               text = paste('Date:', format(date(dates),'%m/%d'),
                            '<br>Cases:', N_cases)),
           stat = 'identity', color = '#145DA0', fill = '#145DA0') +
        xlab('Date') +
        ylab('Positive Tests Per Day') +
        scale_x_date(date_breaks = '2 days', date_labels = '%b %d',
                     expand = c(0,0)) +
        theme(axis.text.x = element_text(angle = 45))

convert_to_interactive(plot_histogram, 0)
```

### Cases per week
**Total cases in a rolling 7-day period.**
```{r plot-rolling-7d-sum}
rolling <- calculate_rolling(7, sum)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       -2, max(rolling$cases) + 15)

plot_rolling_7d_sum <- base_plot +
  geom_point(data = rolling, aes(x = dates, y = cases,
                                 text = paste('Dates:',
                                    paste0(format(date(dates)-6,'%m/%d'),
                                           '-',
                                           format(date(dates),'%m/%d')),
                                    '<br>Cases/week:', cases)),
             color = 'black') +
  ylab('Total Positive Tests, 7 day period')

convert_to_interactive(plot_rolling_7d_sum, 90)
```

### Average cases/day (7 day)
**Mean cases-per-day in a rolling 7-day period.**
```{r plot-rolling-7d-mean}
rolling <- calculate_rolling(7, mean)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       0, max(rolling$cases) + 2)

plot_rolling_7d_mean <- base_plot +
  geom_point(data = rolling, aes(x = dates, y = cases,
                                 text = paste('Dates:',
                                      paste0(format(date(dates)-6,'%m/%d'),
                                           '-', 
                                           format(date(dates),'%m/%d')),
                                    '<br>Cases/day:', round(cases, 2))),
             color = 'black') +
  ylab('Mean Positive Tests/Day, 7 day period')
     
convert_to_interactive(plot_rolling_7d_mean, 90)
```

### Positivity rate (7 day)
**Positivity rate (total positives / total tests) in a rolling 7-day period.**
```{r plot-rolling-7d-positivity}

rolling <- calculate_rolling(7, sum) %>%
  mutate(positivity_rate = rolling$cases / rolling$tests * 100)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       -0.05, max(rolling$positivity_rate) + 0.2)

plot_rolling_7d_positivity <- base_plot +
  geom_point(data = rolling,
             aes(x = dates, y = positivity_rate,
                 text = paste('Dates:',
                              paste0(format(date(dates)-6,'%m/%d'),
                                     '-', 
                                     format(date(dates),'%m/%d')),
                              '<br>Positivity rate:',
                              paste0(round(positivity_rate, 2),
                                     '%'))),
             color = 'black') +
  ylab('Positivity Rate, 7 day period')
  
convert_to_interactive(plot_rolling_7d_positivity, 90)
```

### Cases per 14 days
**Total cases in a rolling 14-day period.**
```{r plot-rolling-14d-sum}
rolling <- calculate_rolling(14, sum)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       -2, max(rolling$cases) + 15)

plot_rolling_14d_sum <- base_plot +
  geom_point(data = rolling,
             aes(x = dates, y = cases,
                 text = paste('Dates:',
                              paste0(format(date(dates)-13,'%m/%d'),
                                     '-', 
                                     format(date(dates),'%m/%d')),
                              '<br>Cases:', cases)),
             color = 'black') +
  ylab('Total Positive Tests, 14 day period')
  
convert_to_interactive(plot_rolling_14d_sum, 90)
```

### Average cases/day (14 day)
**Mean cases-per-day in a rolling 14-day period.**
```{r plot-rolling-14d-mean}
rolling <- calculate_rolling(14, mean)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       0, max(rolling$cases) + 2)

plot_rolling_14d_mean <- base_plot +
  geom_point(data = rolling,
             aes(x = dates, y = cases,
                 text = paste('Dates:',
                              paste0(format(date(dates)-13,'%m/%d'),
                                     '-', 
                                     format(date(dates),'%m/%d')),
                              '<br>Cases/day:', round(cases, 2))),
             color = 'black') +
  ylab('Mean Positive Tests/Day, 14 day period')
  
convert_to_interactive(plot_rolling_14d_mean, 90)
```

### Positivity rate (14 day)
**Positivity rate (total positives / total tests) in a rolling 14-day period.**
```{r plot-rolling-14d-positivity}
rolling <- calculate_rolling(14, sum) %>%
  mutate(positivity_rate = rolling$cases / rolling$tests * 100)

base_plot <- plot_base(min(rolling$dates)-0.5, max(rolling$dates)+0.5,
                       0, max(rolling$positivity_rate) + 0.2)

plot_rolling_14d_positivity <- base_plot +
     geom_point(data = rolling,
                aes(x = dates, y = positivity_rate,
                    text = paste('Dates:',
                                 paste0(format(date(dates)-13,'%m/%d'),
                                        '-', 
                                        format(date(dates),'%m/%d')),
                                 '<br>Positivity rate:',
                                 paste0(round(positivity_rate, 2),
                                        '%'))),
                color = 'black') +
  ylab('Positivity Rate, 14 day period')

convert_to_interactive(plot_rolling_14d_positivity, 90)
```
